Items

### 2023-03-01 items.rmd
- added toc to items

---
title: "Items"
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#       toc_depth: 3
output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---

>>>>

---
title: "Items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---
